%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8

%\documentclass[a4paper, 10 pt, conference]{ieeeconf}  % Comment this line out if you need a4paper

\documentclass[letterpaper, 10pt, conference]{ieeeconf}      % Use this line for a4 paper

\IEEEoverridecommandlockouts                              % This command is only needed if 
                                                          % you want to use the \thanks command

\overrideIEEEmargins                                      % Needed to meet printer requirements.

%In case you encounter the following error:
%Error 1010 The PDF file may be corrupt (unable to open PDF file) OR
%Error 1000 An error occurred while parsing a contents stream. Unable to analyze the PDF file.
%This is a known problem with pdfLaTeX conversion filter. The file cannot be opened with acrobat reader
%Please use one of the alternatives below to circumvent this error by uncommenting one or the other
%\pdfobjcompresslevel=0
%\pdfminorversion=4

% See the \addtolength command later in the file to balance the column lengths
% on the last page of the document

% The following packages can be found on http:\\www.ctan.org
%\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{textcomp}
\usepackage{xurl}
\usepackage{amsmath,bm}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{siunitx}
\usepackage{cite}
\usepackage{psfrag}
\usepackage{multirow}
\usepackage{flushend}

\renewcommand\vec{\mathbf}

\title{\LARGE \bf
On the 3D trochoidal motion model of LiDAR sensors\\placed off-centered inside spherical mobile mapping systems
}

\author{Fabian Arzberger$^{1}$ and Andreas N{\"u}chter$^{1}$% <-this % stops a space
\thanks{$^{*}$We acknowledge funding from the Elite Network Bavaria (ENB) for providing funds for the academic program ``Satellite Technology''}% <-this % stops a space
\thanks{$^{1}$The authors are with Computer Science XVII -- Robotics,
        Julius-Maximilians-Universit{\"a}t W{\"u}rzburg, 97074 Am Hubland, Germany.
        {Contact: \tt\small fabian.arzberger@uni-wuerzburg.de}}%
}


\begin{document}



\maketitle
\thispagestyle{empty}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
We study the motion model of a sensor rigidly mounted inside a ball.
Due to the rigid placement inside the ball, the geometry of the sensor trajectory resembles a 3D curate trochoid.
A new calibration method for spherical systems estimates the extrinsic parameters of the sensor with respect to the balls center of rotation.
We deploy the calibration and motion model on our spherical mobile mapping platform to estimate the trajectory of a LiDAR sensor and compare it to trajectories of state-of-the-art LiDAR-Inertial odometry (LIO) methods.
The motion model, which is solely based on IMU measurements, produces comparable results to the LIO methods, sometimes even outperforming them in positional accuracy.
Although the LIO methods provide better rotational accuracy due to the utilization of LiDAR data, they struggle to reproduce the trochoidal nature of the trajectory and only provide pose estimations at the LiDAR frequency, whereas the motion model produces a more consistent trochoidal trajectory at the much higher IMU frequency.
The results demonstrate the difficulty that current LIO methods have on spherical systems and indicate that our motion model is suitable for overcoming these issues. 
\end{abstract}

\input{sections/01-introduction.tex}
\input{sections/02-related.tex}
\input{sections/03-calibration.tex}
\input{sections/04-model.tex}
\input{sections/05-results.tex}
\input{sections/06-conclusions.tex}

% \begin{appendix}

% \end{appendix}

% \section*{acknowledgment}

\bibliographystyle{ieeetr}
\bibliography{root}

\end{document}
